### 2024-10-09 ms.qmd
Updates

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_complete.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
specie <- c("delicata", "guichenoti")
groups <- c("Red", "Blue")
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(i in 1:length(specie)){
  for(j in 1:length(groups)){
    for(k in 1:length(hormone)){
      for(l in 1:length(temperature)){
        n_list[[paste(specie[i], groups[j], hormone[k], temperature[l], sep = "_")]] <- sample(specie[i], groups[j], hormone[k], temperature[l])
      }
    }
  }
}
```

@@

  labs(y = "Slope estimates", x = "Treatments") +

@@

@@

@@

>>>>

```{r, sampleSize}
#| label: sampleSize
# List with the sample sizes from the database (here("output/databases_clean/data_complete.csv") as the sample size per species and group is the same on each task. We used function sample (see func.R) to estimate the sample size per treatment and species.
source(here("R", "func.R"))
#
hormone <- c("CORT", "Control")
temperature <- c("Cold", "Hot")
#
n_list <- list()
#
for(k in 1:length(hormone)){
  for(l in 1:length(temperature)){
    n_list[[paste(hormone[k], temperature[l], sep = "_")]] <- sample(hormone[k], temperature[l])
  }
}
```

@@

  labs(y = "ROS", x = "Treatments") +

@@

    axis.title = element_text(size = 14, family = "Times"),
    axis.text = element_text(size = 12, family = "Times"),

@@

           hjust = 1.28, vjust = 1.95, size = 4.5, color = "#8D0001")

@@

ggsave("./output/figures/fig_ROS_learning_2.png", plot=plot_ROS_errors, width = 15, height = 10, units = "cm", dpi = 600)
